Followers Are Not Enough: Beyond Structural Communities in Online Social Networks

### 2014-07-24 paper-for_arxiv/results.tex
fixing normalized mutual information figure

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{nmi_singletons.pdf}
\caption{The normalized mutual information between the coverings inferred from the different community types. Community type 0 corresponds to the structural communities, community types 1 through 6 correspond to the activity-based communities with lag 1 through 6 transfer entropies, community type 7 corresponds to the topic-based communities, and community types 8, 9, and 10 correspond to the interaction-based communities using mentions, retweets, and both mentions and retweets. Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity. The normalized mutual information is computed with singletons and orphan nodes included.}
\label{Fig-compare_coverings}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \begin{tabu}{cl}
    \toprule
    Normalized Mutual Information & Community Types \\
    \midrule
    \multirow{8}[8]{*}{\includegraphics[width=0.50\textwidth]{nmi_singletons.pdf}}&0---Structural \bigstrut\\
    &1-6---Activity-Based with Lags 1-6\bigstrut\\
    %&2---Activity-Based with Lag 2\bigstrut\\
    %&3---Activity-Based with Lag 3\bigstrut\\
    %&4---Activity-Based with Lag 4\bigstrut\\
    %&5---Activity-Based with Lag 5\bigstrut\\
    %&6---Activity-Based with Lag 6\bigstrut\\
    &7---Topic-Based \bigstrut\\
    &8---Interaction-Based with Mentions\bigstrut\\
    &9---Interaction-Based with Retweets\bigstrut\\
    &10---Interaction-Based with both \bigstrut\\
    &\,\,\,\,\,\,\,\,\,\,\,\,\,\,Mentions and Retweets\bigstrut\\
    &\bigstrut\\
    \bottomrule
\end{tabu}
\caption{The normalized mutual information between the coverings inferred from the different community types. 
%Community type 0 corresponds to the structural communities, community types 1 through 6 correspond to the activity-based communities with lag 1 through 6 transfer entropies, community type 7 corresponds to the topic-based communities, and community types 8, 9, and 10 correspond to the interaction-based communities using mentions, retweets, and both mentions and retweets. 
Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity. The normalized mutual information is computed with singletons and orphan nodes included.}
\label{Fig-compare_coverings}
\end{figure}
